\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
    \setmainfont{Times New Roman}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin = 1in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Shuofan Zhang, Economics Department},
            pdftitle={Statement of Purpose},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}


  \title{Statement of Purpose}
    \author{Shuofan Zhang, Economics Department}
    \date{}
  
\usepackage{setspace}\singlespacing

\begin{document}

\maketitle


It is my desire to pursue a PhD in Economics at University California,
San Diego as part of my long-term professional goal of becoming an
academic researcher. I have a strong interest in applied econometrics
and macroeconomics.

This passion stemmed from the first econometric course of my master's
program that was taught by Professor Farshid Vahid. I was fascinated by
the idea of tackling real-world problems based on economic theories and
statistical methods, thereby I cannot stop reading the textbook
(Wooldridge 2016). It was then that I discovered three errors in the
equations. Surprised by these errors, Professor Vahid wrote to Professor
Jeffrey Wooldridge, which resulted in for me his appreciation, public
praise in class, and extra course credit points. Encouraged by this
experience, I decided to pursue my interest in econometrics and
transferred my specialization from actuarial studies to applied
econometrics.

In the year that followed, I received the \emph{Student Excellence
Award} for achieving the highest mark in seven out of eight courses. In
April 2018, I was chosen as one of the four representatives of Monash
Business School to participate in the \emph{Econometric Game}\footnote{The
  Econometric Game is hosted by the University of Amsterdam. See
  \url{http://econometricgame.nl/}}, where the best PhD and master
students from thirty prestigious universities including Harvard
University and University of Cambridge study a same question and deliver
academic papers for competition. This year's research topic was around
the detrimental effects of an individual's unemployment on that
individual's happiness as well as on a group's wellbeing. After
reviewing the relevant literature for the empirical support on selecting
explanatory variables, our team constructed an ordered probit model with
the raw responses to the survey item that elicits respondents' overall
life satisfaction as the dependent variable. Under the assumption of the
homogeneous spillover effects amongst individuals in a group, we then
estimated the multiplier between the effects on an individual and a
group. The potential simultaneity bias was discussed. This great
experience of conducting rigorous research provided me with important
new insights into how unemployment affects well-being, and significantly
stimulated my interest in empirical research in economics.

Measures of happiness, previously psychologists' tools, now are widely
used by economists; likewise, statisticians' findings are infiltrating
econometrics.

As an attempt to introduce a statistical technique to econometrics, my
master's thesis employed deep learning to facilitate the hypothesis test
design, which was supervised by Professor Dianne Cook. Deriving
hypothesis tests and the asymptotic distributions constitute a
considerable part of the econometric literature. However, the derivation
is often complex and the resulting test may be powerless. For example,
the Hausman tests and the unit root tests all suffer from low power. In
my thesis, I trained a binary deep learning classifier to detect linear
relationships from no structure in a scatter plot as an alternative to
the conventional \(t\)-test. Tested on a large unseen dataset, the power
(\(1-\beta\)) of the classifier was always close to the \(t\)-test
holding the type I error (\(\alpha\)) constant. Given that the
\(t\)-test is the known uniformly most powerful test under such
experimental settings (Neyman and Pearson 1933), this finding suggests
the deep learning model has the potential to approach the unknown best
test in more complicated situations. The study was then extended to test
the null of homoscedasticity against heteroscedasticity using the
retrained classifier. A small dataset of human evaluations was collected
via an online questionnaire (Majumder, Hofmann, and Cook 2013) and a
specific form of the White test (White 1980) was applied to provide a
reference level of the test accuracy. The classifier achieved much
higher accuracy than both the White test and humans. Using the data plot
as the test statistic instead of a single quantity, this approach could
avoid complex derivations while exploiting the useful information in the
plots (Anscombe 1973). Although the training design could be
challenging, these results empower future research. For instance, by
replacing the scatter plot with time plots one can use this approach to
test the unit root in time series. I am currently writing a first-author
paper on these results to submit to the \emph{Statistical Analysis and
Data Mining}. This study was also presented by Professor Cook as the
\(50^{th}\) \emph{Belz} Lecture for the \emph{Statistical Society of
Victoria}\footnote{The Victorian Branch of the Statistical Society of
  Australia Inc. See \url{https://www.statsoc.org.au/branches/victoria/}}.

After completing the master degree, I was excited to accept an offer
from Professor Heather Anderson and Professor Farshid Vahid as a
research assistant to work on a paper that studying the high-dimensional
predictive regression with the LASSO\footnote{LASSO is the abbreviation
  for Least Absolute Shrinkage and Selection Operator.} (Koo et al.
2016). In this project, I reviewed the literature to investigate the
compatibility (or restricted eigenvalue) condition and its implication
of choosing the tuning parameter \(\lambda\) for the \(\ell_1\) norm to
achieve the prediction optimality, while taking into account the
potential consequences of inconsistency for variable selection by the
LASSO (Bühlmann and Van De Geer 2011). I have been self studying Real
Analysis by reading the book \emph{Principles of Mathematical
Analysis}(Rudin 1976) to better understand the relevant concepts.
Comparison between the LASSO, the adaptive LASSO and the group LASSO is
under considering. In addition, the out-of-sample mean squared errors of
forecasting GDP growth and inflation rate using the LASSO on 146
macroeconomics variables are compared against other approaches including
an autoregressive model and a principal component analysis. The
potential co-integrating relationships in the selected variables are
being studied. Observing the series chosen by this data-driven
methodology and seeking possible economic theory-based explanations are
intriguing and encourage me to learn more. I want to continue to work on
macroeconomic problems and apply cutting-edge techniques to challenging
areas such as high-dimensional data and forecasting economic or
financial series.

Meanwhile, I am co-authoring a paper with the Learning and Teaching team
at Monash University that measuring student levels of perceptions of
live-streaming, a new technology implemented in the lectures. Our study
adapted the CRiSP\footnote{CRiSP is the name of classroom response
  system perceptions questionnaire.} questionnaire (Richardson et al.
2015) which was validated by a combination of factor analyses. Results
revealed three reliable scales: acceptance, usability, and confidence.
Following the validation results, I have investigated the correlations
between student perceptions of live-streaming and their study attitudes
using the estimated factor scores. The treatment effect of
live-streaming on students academic performance is also being studied by
the fixed effects model with panel data accounting for the unobserved
heterogeneity.

Though I am open to a variety of research in Economics, I find the work
of Professor Elliott, Timmermann, and Hamilton are especially
interesting to me. I am confident that my talent in Mathematics combined
with my various research experiences in Economics will allow me to
contribute positively to the PhD program at University California, San
Diego.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-ANS73}{}
Anscombe, FJ. 1973. ``Graphs in Statistical Analysis.'' \emph{The
American Statistician} 27 (1): 17--21.

\hypertarget{ref-buhlmann}{}
Bühlmann, Peter, and Sara Van De Geer. 2011. \emph{Statistics for
High-Dimensional Data: Methods, Theory and Applications}. Springer
Science \& Business Media.

\hypertarget{ref-koo}{}
Koo, Bonsoo, Heather M Anderson, Myung Hwan Seo, and Wenying Yao. 2016.
``High-Dimensional Predictive Regression in the Presence of
Cointegration.''

\hypertarget{ref-MM13}{}
Majumder, Mahbubul, Heike Hofmann, and Dianne Cook. 2013. ``Validation
of Visual Statistical Inference, Applied to Linear Models.''
\emph{Journal of the American Statistical Association} 108 (503). Taylor
\& Francis Group: 942--56.

\hypertarget{ref-Neyman289}{}
Neyman, J., and E. S. Pearson. 1933. ``IX. on the Problem of the Most
Efficient Tests of Statistical Hypotheses.'' \emph{Philosophical
Transactions of the Royal Society of London A: Mathematical, Physical
and Engineering Sciences} 231 (694-706). The Royal Society: 289--337.
doi:\href{https://doi.org/10.1098/rsta.1933.0009}{10.1098/rsta.1933.0009}.

\hypertarget{ref-crisp}{}
Richardson, Alice M, Peter K Dunn, Christine McDonald, and Florin
Oprescu. 2015. ``CRiSP: An Instrument for Assessing Student Perceptions
of Classroom Response Systems.'' \emph{Journal of Science Education and
Technology} 24 (4). Springer: 432--47.

\hypertarget{ref-rudin}{}
Rudin, Walter. 1976. ``Principles of Mathematical Analysis
(International Series in Pure \& Applied Mathematics).'' McGraw-Hill
Publishing Co.

\hypertarget{ref-white}{}
White, Halbert. 1980. ``A Heteroskedasticity-Consistent Covariance
Matrix Estimator and a Direct Test for Heteroskedasticity.''
\emph{Econometrica: Journal of the Econometric Society}. JSTOR, 817--38.

\hypertarget{ref-wooldridge2016}{}
Wooldridge, Jeffrey M. 2016. \emph{Introductory Econometrics: A Modern
Approach, 6th Edition}. Cengage.

\end{document}
